An Open-Source Implementation of the CMPS Algorithm for Assessing Similarity of Bullets

### 2021-10-14 ju-hofmann/ju-hofmann.Rmd

The automated framework used in this paper was proposed by @aoas.
In order to obtain bullet signatures from the x3p files of bullet land engravings, we use the `R` packages \pkg{x3ptools} [@x3ptools] and \pkg{bulletxtrctr} [@bulletxtrctr].
\pkg{x3ptools} is a package to read, write, and generally, process x3p files.
The \pkg{bulletxtrctr} package implements a pipeline for extracting and comparing signatures from scans of land-engraved areas.

>>>>

The automated framework for extracting signatures from x3p files used in this paper was proposed by @aoas and is implemented in the `R` packages \pkg{x3ptools} [@x3ptools] and \pkg{bulletxtrctr} [@bulletxtrctr].
\pkg{x3ptools} is a package to read, write, and generally, process x3p files.
The \pkg{bulletxtrctr} package implements a pipeline for extracting and comparing signatures from scans of land-engraved areas.
